stupid backoff

### 2019-11-30 al_stup.Rmd
server

```{r}
library(quanteda)
library(dplyr)
library(stringr)
library(wordcloud)
library(data.table)
library(readtext)
library(spacyr)
library(ggplot2)

@@

#takin 15% of data for memory reasons
set.seed(1)
x = sample(2360148, 590037, replace = F)

@@

unigs = getTables(TW, 1)
bigrs = getTables(TW, 2)
trigs = getTables(TW, 3)
quads = getTables(TW, 4)
rm(TW)
gc()
```

>>>>

```{r}
library(quanteda)
library(dplyr)
library(stringr)
library(wordcloud)
library(data.table)
library(readtext)
library(spacyr)
library(ggplot2)
library(sqldf)
```

@@

#takin 15% of data for memory reasons
set.seed(1)
x = sample(2360148, 300000, replace = F)

@@

unigs = getTables(TW, 1)
unigsfull = getTablesRM(TW, 1)
bigrs = getTables(TW, 2)
trigs = getTables(TW, 3)
rm(TW)
gc()
```
